### 2019-08-22 maciek.tex
Omega(kl)

  \begin{enumerate}
    \item Cluster A component of size k-1. Define x.
    \item The input sequence (after these glueing) is to keep asking for x and someone of x's color
    \item Define a sequence of xs for any deterministic algorithm.
    \item Define what OPT should do: the cluster D and nodes d1 d2 that should be hidden from the sequence of xs?)
    \item (somewhere) define c(x): it is easy when x is not from D: then any would do; if x is from D, then issue request between non-d1/d2; also not defined for a1,ak-1, b1,bk-1 and ak, bk
    \item Argue that OPT does not pay for input sequence (after glueing)
    \item lower-bound the number of times we can issue (x, c(x)) request; until it encounters either d1 or d2 in place of x; this is lower-bounded by the total number of nodes-2 (d1 and d2 are last? they cannot be, though, but the furthest away should be at min distance k*l/2)
    \item also, this k*l/2 sequence is feasible, as the perfect partition exists: we can always issue this request (unless d1d2)
    \item the total cost of ALG, comp ratio
  \end{enumerate}

  Fix a deterministic algorithm DET.
  Fix a cluster $A$ containing nodes $a_1, \ldots, a_k$ and a cluster $B$ containing (among others) a node $b$.
  The adversary begins with issuing $k-2$ internal requests $(a_i, a_{i+1})$, so that nodes $a_1, \ldots a_{k-1}$ form a single component.
  The internal requests are free for OPT, and it doesn't perform additional actions at this point.

  \maciek{Possibly we need a better name than $x$. Something that indicates that this changes over time, possibly tied to the name DET.}
  We define $x$ to be the node in the configuration of DET that is co-located in one cluster with the component $a_1, \ldots, a_{k-1}$.
  Initially, $x = a_k$.

  Then, the adversary issues an external request $(x, b)$, which at this point is the request $(a_k, b)$.
  Note that DET must relocate the component $\{a_k, b\}$ to some other cluster.
  OPT also relocates the component $\{a_k, b\}$ to some carefuly chosen cluster $D$ (to be fixed later), and it migrates nodes $d_1$ and $d_2$ to the previous locations $a_k$ and $b$ (i.e., to the clusters $A$ and $B$).

  Now, for a node $p$ we define $c(p)$ in the following way: for each node outside of $a_i$ and $b$, we define $c(p)$ to be any node that in the initial configuration was placed at the same cluster as $p$, and if $p$ belonged to $D$, then $c(p)$ is any such node that is different from $d_1$ and $d_2$.
  \maciek{we have a cyclic reference at this point. D is not yet defined (depends on c), and c depends on d1, d2...}
  Then, the adversary continues to issue requests $(x, c(x))$.
\end{proof}

@@

\maciek{The most recent version of the lower bound is in $\Omega(l\cdot k)$ section. This is an early version!}

>>>>

  \maciek{cluster B is special?}
  \maciek{If DET splits a component, we issue intra-component requests until DET joins it}

  Fix a deterministic algorithm DET.
  Fix a cluster $A$ containing nodes $a_1, \ldots, a_k$ and a cluster $B$ containing (among others) a node $b_1$.
  The adversary begins with issuing $k-2$ internal requests $(a_i, a_{i+1})$, so that nodes $a_1, \ldots a_{k-1}$ form a single component.
  The internal requests are free for OPT, and it doesn't perform additional actions at this point.
  The next request issued by the adversary is an external request $(a_k, b_1)$.%, which at this point is the request $(a_k, b)$.
  Note that DET must relocate the component $\{a_k, b_1\}$ to some other cluster.
  OPT also relocates the component $\{a_k, b_1\}$ to some carefuly chosen cluster $D$, and it evicts nodes $d^{(1)}$ and $d^{(2)}$ (to be fixed later) from $D$ to the previous locations of $a_k$ and $b_1$ (i.e., to the clusters $A$ and $B$).
  For these actions, OPT pays $2$, and DET pays at least $2$.
  We name the requests issued so far as $I_1$.

  Now, we construct a sequence of requests $I_2$, but we do not feed them to DET yet.
  Instead, we simulate DET's actions on $I_1I_2$ to terminate the input sequence earlier, i.e., we choose a prefix $I_2'$ of $I_2$ and we feed DET the input $I_1I_2'$.
  \maciek{We can produce $I_2'$ on-the-fly, but this was convinient to write it down this way}

  The input $I_2$ consists of requests $(x^{(1)}, y^{(1)}), (x^{(2)},y^{(2)}),\ldots$.
  The node $x^{(i)}$ is a node in the current configuration of DET that is co-located in one cluster with the component $a_1, \ldots, a_{k-1}$.
  After a request $(x^{(i)}, y^{(i)})$, the node $x^{(i)}$ is a part of a non-singleton component and must be relocated to some other cluster (as its current cluster hosts a component $a_1, \ldots, a_{k-1}$).
  Then, DET places the node $x^{(i+1)}$ in place of $x^{(i)}$, and the next request concerns that node.
  % Initially, $x^{(1)} = a_k$, and the next node $x^{(2)}$ is the that DET locates in place of the

  For each $x^{(i)}$, we set $y^{(i)}$ to some node that in the intial configuration was co-located with $x^{(i)}$.

  Note that in the initial configuration, nodes of one cluster are indistinguishible for DET \maciek{and hence we can order them on-the-fly}.

  Now, we formally fix nodes $y^{(i)}$.
  Consider a set of nodes from an initial configuration of a cluster $C$ (where $C \neq A, C \neq B$).
  Formally, by $v^C_1$ we label the first node of a cluster $C$ that appears in the sequence of $x$'es at the position $i$.
  At this point, we choose an arbitrary other node of $C$ and we label it $v^C_0$.
  We set $y^{(i)} = v^C_0$.
  For the following $k-2$ nodes of the cluster $C$, we label them $v^C_2, v^C_3, \ldots$ in the order of appearance in the sequence of $x$'es.
  For a node $v^C_j = x^{(i)}$, we set $y^{(i)} = v^C_0$.
  Some nodes of $C$ might never appear in the sequence of $x$'es, and we number them arbitrarily (with the restriction that the nodes that appear in the sequence of $x$'es have smaller number than the ones that did not).

 % During the runtime of DET, by $x(A)$ we denote the node in the configuration of DET that is co-located in one cluster with the component $a_1, \ldots, a_{k-1}$.

 % \maciek{Possibly we need a better name than $x(A)$. This should be tied to (1) DET, and (2) the component $a_1, \ldots, a_{k-1}$ (not the server A, from which it might be relocated by DET). Maybe we should number them, i.e., $x_1, x_2,\ldots$}
 % During the runtime of DET, by $x(A)$ we denote the node in the configuration of DET that is co-located in one cluster with the component $a_1, \ldots, a_{k-1}$.
 % Initially, $x(A) = a_k$.

 % We consider a sequence of requests between a node $x(A)$ and some other nodes, i.e., each request concerns the node that is currently co-located with the component $a_1,\ldots,a_{k-1}$.
 % As a result

  Fix a node $m^C$ for each cluster $C$.

  % Note that nodes of one cluster are indistinguishible for DET.

 % For the purpose of constructing $I_2$, we order nodes of any cluster $C$: $v^C_1, \ldots, v^C_k$.
 % For any node $v^C_i\neq v^C_1$ we define $c(v^C_i) = v^C_1$, and $c(v^C_1) = v^C_2$.

  %Now, for a node $p$ we define $c(p)$ in the following way: for each node outside of $a_i$ and $b$, we define $c(p)$ to be any node that in the initial configuration was placed at the same cluster as $p$, and if $p$ belonged to $D$, then $c(p)$ is any such node that is different from $d_1$ and $d_2$.
  %\maciek{we have a cyclic reference at this point. D is not yet defined (depends on c), and c depends on d1, d2...}
  %Then, the adversary continues to issue requests $(x, c(x))$.
\end{proof}

@@

\maciek{The most recent version of the lower bound is in $\Omega(l\cdot k)$ section. This is an early version!}
  \begin{enumerate}
    \item Cluster A component of size k-1. Define x.
    \item The input sequence (after these glueing) is to keep asking for x and someone of x's color
    \item Define a sequence of xs for any deterministic algorithm.
    \item Define what OPT should do: the cluster D and nodes d1 d2 that should be hidden from the sequence of xs?)
    \item (somewhere) define c(x): it is easy when x is not from D: then any would do; if x is from D, then issue request between non-d1/d2; also not defined for a1,ak-1, b1,bk-1 and ak, bk
    \item Argue that OPT does not pay for input sequence (after glueing)
    \item lower-bound the number of times we can issue (x, c(x)) request; until it encounters either d1 or d2 in place of x; this is lower-bounded by the total number of nodes-2 (d1 and d2 are last? they cannot be, though, but the furthest away should be at min distance k*l/2)
    \item also, this k*l/2 sequence is feasible, as the perfect partition exists: we can always issue this request (unless d1d2)
    \item the total cost of ALG, comp ratio
  \end{enumerate}
